Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-26 manuscript/manuscript.tex
Changes in manuscript

\begin{equation}
    \rho(r') = A \left( e^{-(r' - R)/b} - 1\right) + 2670 \text{kg/m}^3,
\label{eq:density-exp}
\end{equation}
\noindent where
\begin{equation}
    A =
    (3300 \text{kg/m}^3 - 2670 \text{kg/m}^3)
    \left( e^{( R_2 - R_1 )/b} - 1 \right)^{-1},
\end{equation}

\noindent and the value of $b$ equal to the thickness of the spherical shell we use to perform the test.
In this way, the density function assumes the values of 2670 kg/m$^3$ and 3300 kg/m$^3$ on the shell's outer and inner radii, respectively.
The analytical solution of the gravity potential is easily obtained as the sum of the ones for a pure exponential function and for an homogeneous spherical shell.

@@

Firstly, lets assume a symmetric density function, i.e. $R_c=(R_1 + R_2)/2$ is the centre radius of the shell, and perform the test for a thin shell of 1km of thickness without applying the density-based discretization algorithm.
The results can be seen in Figure \ref{fig:D-discont-sym}.
Once again, we obtain good accuracy for values of $D$ equal to 1, 2 and 8 for the computation of the potential, the gradient components and the Marussi tensor components, respectively.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/discontinuous-D-sym.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the discontinuous density defined on equation \ref{eq:density-discontinuous} and $R_c$ as the centre radius of the shell. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-discont-sym}
\end{figure}

Secondly, lets assume the same density function from equation \ref{eq:density-discontinuous}, but now with an asymmetrical distribution: $R_c = (R_1 + R_2)/3$, and perform the same test.
We can see its results in Figure \ref{fig:D-discont-asym}: up to $D=10$ the difference between the numerical model and the analytical solution is greater than 10\%, what
leads us to conclude that a density-based discretization algorithm is needed in order to guarantee the accuracy of the model.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/discontinuous-D-asym.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the discontinuous density defined on equation \ref{eq:density-discontinuous} and $R_c=(R_1 + R_2)/3$. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-discont-asym}
\end{figure}

>>>>

\begin{equation}
    \rho(r') = A e^{-(r' - R)/b} + C,
\label{eq:density-exp}
\end{equation}
\noindent where
\begin{equation}
    A =
    (3300 \text{kg/m}^3 - 2670 \text{kg/m}^3)
    \left( e^{( R_2 - R_1 )/b} - 1 \right)^{-1},
\end{equation}
\begin{equation}
    C =
    2670 \text{kg/m}^3 - A,
\end{equation}

\noindent and the value of $b$ equal to the thickness of the spherical shell we will use to perform the test.
In this way, the density function assumes the values of 2670 kg/m$^3$ and 3300 kg/m$^3$ on the shell's outer and inner radii, respectively.
The analytical solution of the gravity potential is easily obtained as the sum of the ones for a pure exponential function and for an homogeneous spherical shell.

@@

Lets assume that $R_c = (R_1 + R_2)/3$ and perform the test for a thin shell of 1km of thickness without applying the density-based discretization algorithm.
Its results can be seen in Figure \ref{fig:D-discont-asym}: up to $D=10$ the difference between the numerical model and the analytical solution is greater than 10\%, what leads us to conclude that a density-based discretization algorithm is needed in order to guarantee the accuracy of the model.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/discontinuous-D-asym.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the discontinuous density defined on equation \ref{eq:density-discontinuous}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-discont-asym}
\end{figure}
